\setstretch{1.5}
We would like to express our sincere gratitude to our supervisor, \textbf{Dr. Hussein El-Taeibe Sleem}, for their invaluable guidance, support, and expertise throughout the entire process of conducting this research. Their insightful feedback and encouragement greatly contributed to the success of this thesis.

We also extend our heartfelt appreciation to \textbf{families and friends} for their unwavering support and encouragement during this academic journey. Their constant belief in our abilities and their understanding of the demands of this endeavor have been instrumental in our perseverance and accomplishment.

Furthermore, we would like to express our sincere appreciation for the resources and facilities provided by \textbf{Valeo Egypt}. We are grateful to our mentor, \textbf{Eng. Enas Atef}, for her invaluable guidance and support throughout the entire research process. We also extend our thanks to the Graduation Project Support Program Coordinator, \textbf{Dr. Neveen Abdelkader}, and Valeo Academy Program Manager, \textbf{Eng. Osama Shaaban}, for their support.The access to technical materials, support training sessions with experts, and provision of electronic equipment greatly enhanced the quality of our study. We are grateful for the opportunities provided through the Techie Fellowship Program, which added significant value to our team's skills in Embedded Software Development.

Lastly, we are thankful to all the individuals who have contributed in various ways, be it through discussions, suggestions, or constructive criticism, that have shaped the development of this thesis. Your contributions have been invaluable in refining the ideas and arguments presented here.